---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```

# webmorph

<!-- badges: start -->
<!-- badges: end -->

The goal of webmorph is to integrate with [webmorph.org](https://webmorph.org).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("facelab/webmorph")
```

```{r setup}
library(webmorph)
```


## Load your images

```{r}
path <- system.file("extdata/composite/", 
                    package = "webmorph")

temlist <- read_tem(path, pattern = "multi\\.tem")
```

The lines are currently plotted as straight lines, but Lisa will add in the proper bezier curves soon.

```{r, out.width = "100%", fig.width = 8, fig.height = 4, fig.cap="Original Images and Templates"}
plot(temlist, images = TRUE, line.plot = TRUE)
```

## Delete some points

```{r, out.width = "100%", fig.width = 8, fig.height = 4, fig.cap="Point removal"}

remove_points <- frl_features("imprecise")
temlist %>%
  pt_delete(remove_points) %>%
  plot(pt.shape = "index", 
       pt.colour = "black", 
       line.plot = TRUE, 
       line.colour = c("red", "orange", "yellow", 
                       "green", "blue", "purple"))
```


## Rotate

```{r, out.width = "100%", fig.width = 8, fig.height = 4, fig.cap="Rotated Images and Templates"}
temlist %>%
  rotate(45) %>%
  plot(images = TRUE)
```


## Crop

You can set the new width, height, x-offset and y-offset in pixels (must be > 2) or proportions.

```{r, out.width = "100%", fig.width = 6, fig.height = 4, fig.cap="Cropped Images and Templates"}
temlist %>%
  crop(width = .6, height = .8, 
       x_off = .2, y_off = .1) %>%
  plot(images = TRUE)
```


```{r, out.width = "100%", fig.width = 8, fig.height = 4, fig.cap="Cropped Images and Templates"}
temlist %>%
  crop(width = 1.2, height = 1.2, 
       x_off = -0.1, y_off = -0.1,
       fill = "hotpink") %>%
  plot(images = TRUE)
```

## Chaining

You can also chain image manipulation commands.

```{r, out.width = "100%", fig.width = 8, fig.height = 4, fig.cap="Manipulated Images and Templates"}
temlist %>%
  rotate(45) %>%
  crop(.5, .5, .25, .25) %>%
  plot(images = TRUE)
```


## Fun things

You can do some more fun things to the images (but not templates) with the {magick} package that is installed with {webmorph}.

```{r, out.width = "100%", fig.width = 6, fig.height = 4}
image <- temlist[[1]]$img

imglist <- list(
  magick::image_blur(image, radius = 10, sigma = 5),
  magick::image_charcoal(image, radius = 5, sigma = 2),
  magick::image_oilpaint(image, radius = 10),
  magick::image_implode(image, factor = 0.25),
  magick::image_implode(image, factor = -0.25),
  magick::image_negate(image)
)

labs <- c("Blur", "Charcoal", "Oilpaint", 
          "Implode", "Explode", "Negate")

lapply(imglist, magick::image_ggplot) %>%
  cowplot::plot_grid(plotlist = ., nrow = 2,
                     labels = labs)

```
