---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# webmorphR

<!-- badges: start -->
<!-- badges: end -->

The goal of webmorphR is to integrate with [webmorph.org](https://webmorph.org).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("facelab/webmorphR")
```
## Example

Load in all the tems from a directory. The code below loads images built into webmorphR from the CC-BY licensed [Young Adult Composite Faces](https://doi.org/10.6084/m9.figshare.4055130.v1).

```{r example}
library(webmorphR)

path <- system.file("extdata/test", package = "webmorphR")
stimlist <- read_stim(path)
```

You can plot an image with the `plot()` function.

```{r basic-plot, fig.width = 8, fig.height = 4}
plot(stimlist, line.plot = TRUE)
```

## Reproducible stimulus construction

Load faces from the CC-BY licensed [Face Research Lab London Set](https://doi.org/10.6084/m9.figshare.5047666.v3).

```{r}
face_set <- faces("london")[5:7]%>%
  rename(prefix = "orig_", pattern = "_03", replacement = "")

stimuli <- face_set %>%
  mirror(frl_sym()) %>%
  rename(pattern = "orig", replacement = "mirror") %>%
  c(face_set, .) %>%
  resize(1/3) %>%
  crop(0.6, 0.8) %>%
  crop(1.05, 1.05, fill = rainbow(3)) 
```

Save your stimuli

```{r, eval = FALSE}
write_stim(stimuli, dir = "mystimuli")
```


Easily create figures to illustrate your research.

```{r repro-plot, fig.width = 9, fig.height = 8}
plot(stimuli, nrow = 2)
```

