---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# webmorph

<!-- badges: start -->
<!-- badges: end -->

The goal of webmorph is to integrate with [webmorph.org](https://webmorph.org).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("facelab/webmorph")
```
## Example

Load in all the tems from a directory. The code below loads images built into {webmorph} from the CC-BY licensed [Face Resaerch Lab London Set](https://doi.org/10.6084/m9.figshare.5047666.v3).

```{r example}
library(webmorph)
## basic example code

path <- system.file("extdata/demo", package = "webmorph")

tems <- read_tem(path, pattern = "00._03\\.tem")
```

You can plot an image with the `plot()` function.

```{r, out.width = "50%", fig.width = 3, fig.height = 3}
plot(tems$`001_03`, image = TRUE)
```


```{r, out.width = "100%", fig.width = 9, fig.height = 9}
plots <- lapply(tems, plot, 
                color = "blue",
                image = TRUE)

cowplot::plot_grid(plotlist = plots,
                   labels = names(tems))
```


You can also visualise just the templates. If you omit the image and don't manually set a width and height, the x- and y-axis limit will be set automatically.

```{r, out.width = "100%", fig.width = 9, fig.height = 9}
plots <- lapply(tems, plot, 
                color = "#FF0000",
                pt.size = 2,
                pt.shape = 1,
                bg.fill = "black",
                image = FALSE)

cowplot::plot_grid(plotlist = plots,
                   labels = names(tems))
```
