---
title: "Making Figures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Making Figures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)

starttime <- Sys.time()
```

```{r setup}
library(webmorphR)
```

WebmorphR has plotting functions to make it easier to create reproducible figures from your stimuli. 

```{r}
stim <- faces("test")
```

If you don't set any arguments apart from the stimulus list, the result will be a ggplot object that will be displayed using the default or chunk figure dimensions.

```{r}
plot_fig(stim)
```

Due to an annoying problem with how RStudio displays text in plots in R Markdown files when you run code chunks interactively versus knit them, `plot_fig()` allows you to set the width and height of the figure (in inches, but you can change this with the `units` argument). Then it will render the image as file and return the output of `knitr::include_graphics()`. You can optionally set a filename to save the file.

```{r}
plot_fig(stim, width = 7, height = 3.5, 
         filename = "fig/fig_test.png")
```

## Borders and Background

You can add a border to each image. Values less than 1 will set border width as a percentage of the image width, while values greater than 1 will set it as pixels (relative to original image size). You can also change the border colour.

```{r}
plot_fig(stim, 7, 3.5, border.width = 0.05, border.color = "hotpink")
```

You can set different border sizes for the top, right, bottom and left sides (think "TRouBLe"). This can be useful for creating space for labels outside the image.

```{r}
plot_fig(stim, 7, 4, border.width = c(.1, 0, 0, 0),
         border.color = "black",
         label.color = "white",
         label.y = 1.05, vjust = 0.5)
```

You can set the border colour separately for each image. Set a margin (in `units`, defaults to 0.1 inches) and background colour to separate panels.

```{r}
plot_fig(stim, 7, 4, 
         border.width = c(0.2, 0, 0, 0),
         border.color = c("#F9DEC9", "#BAEDDD"), 
         labels = c("Average Woman", "Average Man"),
         label.color = c("#946319", "#1A9178"),
         label.y = 1.1, vjust = 0.5,
         margin = 0.2, bg.color = "grey20")
```


## Delineations

Set `pt.plot` and/or `line.plot` to TRUE to show the delineations. By default, points are green pluses and lines are translucent yellow.

```{r}
plot_fig(stim, 7, 3.5, pt.plot = TRUE, line.plot = TRUE)
```

You can change the default colours and translucency with the `colour` and `alpha` arguments, or set separate ones for labels, points and lines by prefixing the with `label.`, `pt.` and `line.`. Specific aesthetics override the general ones.

```{r}
plot_fig(stim, 7, 3.5, img.plot = FALSE, pt.plot = TRUE, line.plot = TRUE,
         colour = "blue",
         pt.shape = 1,
         line.color = "red",
         alpha = 1)
```

You can set line.plot to "bezier" to show curved lines, but this takes a long time and isn't quite right yet. (Calculating bezier curves is harder than you'd think.)

```{r}
rb <- rainbow(6, v = 0.5, start = 0.2)
plot_fig(stim, 7, 3.5, img.plot = FALSE, 
         line.plot = "bezier", line.color = list(rb))
```

## Delete some points

```{r, fig.cap="Point removal"}
remove_points <- frl_features("imprecise")
stim %>%
  pt_delete(remove_points) %>%
  plot_fig(8, 4,
    pt.shape = "index", 
    pt.colour = "black", 
    line.plot = TRUE, 
    line.colour = list("green", rainbow(6)))
```

## Labels

By default, figure panels are labelled with the image name. Set `labels = ""` to remove labels. 

```{r}
plot_fig(stim, 7, 3.5, labels = "")
```

Use the `rename()` function to set new names or set labels to a vector of labels to use.

```{r}
faces("composite") %>%
  rename(pattern = "f_", replacement = "Female ") %>%
  rename(pattern = "m_", replacement = "Male ") %>%
  plot_fig(10, 4, nrow = 2)
```

Labels can be positioned with the `label.position` argument, which takes one value for the vertical position (top, middle, bottom) and one value for the horizontal position (left, center, right).

```{r}
plot_fig(stim, 7, 3.5, 
         labels = c("Female", "Male"),
         label.position = "top left",
         label.color = "darkmagenta",
         label.size = 6, 
         label.fontface = "italic")
```

If you want more fine control of label position, you can override the defaults with the arguments hjust, vjust, label.x, label.y and label.angle.

```{r}
plot_fig(stim, 7, 3.5, 
         label.color = "dodgerblue3",
         label.size = 7,
         label.fontface = "bold",
         hjust = 0.5,
         vjust = 0.5,
         label.x = .15,
         label.y = .15,
         label.angle = 360-45)
```


## Word Stimuli

Make word stimuli by starting with blank images. You can specify the size and colour.

```{r}
new_stimuli <- blank(n = 6, width = 100, height = 100, 
                     color = c("red", "orange", "yellow", "green", "blue", "purple"))
```


```{r, echo = FALSE}
plot_fig(new_stimuli, 12, 2, labels = "", nrow = 1)
```

Then you can add words to each stimulus with the `label()` function.

```{r}
colours <- c(red = "red", 
             orange = "darkorange", 
             green = "darkgreen", 
             blue = "blue", 
             purple = "purple")
n <- length(colours)
labels <- rep(names(colours), each = n)

stroop <- blank(n*n, 400, 100) %>%
  label(labels, size = 5, color = colours, 
        position = "center center")
```

```{r, echo = FALSE}
plot_fig(stroop, 3*n, n, ncol = n, labels = "", bg.color = "grey")
```

```{r, echo = FALSE}
elapsed <- (Sys.time() - starttime) %>%
  as.numeric(units="mins") %>%
  round(1)
```

This script took `r elapsed` minutes to render all the included images from scratch.
